Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-10 Manuscript/Manuscript.Rmd
.

p1 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = time, y = abundance, color = protein)) + geom_path() +
  facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "none")

@@

p3 <- rbind(low_cor, high_cor) %>%
  ggplot(., aes(x = ProtA, y = ProtB, color = cor)) + geom_point() +
  stat_ellipse() +
  theme_minimal() +
  theme(legend.position = "none")

p4 <- tibble(cor = c("High Cor","Low Cor"),
       var_sum = c(sqrt(30^2 + 30^2 + 2*0.8*30^2),
                   sqrt(30^2 + 30^2 + 2*0*30^2))) %>%
  ggplot(., aes(x = cor, y = var_sum, fill = cor)) + geom_bar(stat = "identity") +
  theme_minimal() +
  theme(legend.position = "none")

>>>>

p1 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = time, y = abundance, color = protein)) + 
  #annotate("rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, aes(fill = cor)) +
  #geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, aes(fill = cor, color = NA), alpha = 0.002) +
  geom_path() +
  facet_wrap(~cor, ncol = 1) +
  scale_color_manual(values = c("#d53e4f","#3288bd")) +
  theme_minimal() +
  theme(legend.position = "none")

@@

p3 <- rbind(low_cor, high_cor) %>%
  ggplot(., aes(x = ProtA, y = ProtB, color = cor)) + geom_point() +
  scale_color_manual(values = c("#d53e4f","#3288bd")) +
  stat_ellipse() +
  theme_minimal() +
  theme(legend.position = "none")

p4 <- tibble(cor = c("High Cor","Low Cor"),
       var_sum = c(sqrt(30^2 + 30^2 + 2*0.8*30^2),
                   sqrt(30^2 + 30^2 + 2*0*30^2))) %>%
  ggplot(., aes(x = cor, y = var_sum, fill = cor)) + geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#d53e4f","#3288bd")) +
  theme_minimal() +
  theme(legend.position = "none")
